General constraints on magic distillation protocols from statistical mechanics

### 2021-06-02 magic_paper.tex
added form of noisy strange state entropy

Using the above results, we can derive the following entropic bound on magic state transformations. \nick{to be extended (1) from unital processes to general relative majorization, (2) from $\alpha = 2m$ to $\alpha = 2m/(2k+1)$ for integer $m,k \geq 0$, (1) from Strange state to any magic state distillation}

@@

\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}

>>>>

Using the above results, we can derive the following entropic bound on magic state transformations. \nick{to be extended (1) from unital processes to general relative majorization, (2) from $\alpha = 2m$ to $\alpha = 2m/(2k+1)$ for integer $m,k \geq 0$, (3) from Strange state to any magic state distillation}

@@

For an $\epsilon$-noisy Strange state, we have
\begin{equation}
	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
\end{equation}

We also have for any quantum state $\rho$ that
\begin{equation}
	H_{0}\left(\rho\right) = 2\log_2 3 = H_\alpha \left( \id/3 \right),
\end{equation}
for any $\alpha$, so the bound is not well-defined for $H_0$. \nick{this should be true for general relative majorization.}
\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}
